%!TEX root = main.tex

% \begin{verbatim}

Driver actions:

- \action{Roll}: traction interruption, driver searches acceleration such that torque at gearbox == 0.
   if acceleration > 0 and vehicle's speed (driving downhill) > target speed (+ overspeed) => driver strategy has to activate brakes (search braking power to achieve acceleration == 0, torque at gearbox == 0)
   handle gearbox traction interruption time response: compute distance based on remaining time (gearbox) and rolling acceleration.

- \action{Drive}: driver searches acceleration to reach target velocity. Handles engine overload by reducing acceleration (accceleration may become < 0 - e.g., if driving uphill; vehicle can't reach target speed).
  engine under-load => return \cmp{OverloadResponse} (driving strategy should apply brakes).
  engine over-load (engine already at max power, acceleration < braking deceleration - e.g. steep uphill) => return \cmp{OverloadResponse} (driving strategy decides whether to continue (at most until velocity = 0) or abort)

- \action{Coast}: driver searches acceleration to reach engine's full-drag power; engine power < 0.

- \action{Brake}: driver searches for braking power to reach desired acceleration, engine is at full drag load.
    if clutch is open the brakes have to apply more power to compensate loss of engine's drag load (instantaneous); braking power such that torque at gearbox == 0.

Two different Driver Modes:

- \action{DriveMode}: accelerate or keep target speed
	look-ahead, compute action distances (coasting, braking) for upcoming speed reductions. drive at most up to nearest action distance. switch to brake mode if action distance is reached.

	if clutch is open: \action{Roll} (traction interruption)
	else: \action{Drive} -> \action{Brake} (if engine under-load)

- \action{BrakeMode}: decelerate to next target speed.
    start \action{Coasting} at coasting-action distance until braking distance. 
    if coasting deceleration is greater than `look-ahead deceleration' write a WARNING
    re-compute braking-distance for current trigger (distance, next target velocity)
    if braking distance is reached: start \action{Braking} until triggr distance is reached or target velocity is reached.
    if target velocity is reached \action{Drive} until trigger distance.
    if trigger distance is reached switch to \action{DriveMode}

    if clutch is open \action{Coasting} is replaced by \action{Roll}


Gear shift behavior

- gearbox needs to change gears => gear-shift response, required traction interruption time
-> driver processes gear-shift response: switches to \action{Roll} action


% \end{verbatim}